Geometric Information for Image Understanding

### 2018-06-08 chapters/introduction/introduction.tex
finish approaches

\section{Our Approach}
Our approach conver the following area:

@@

  \item \textbf{Extract Geometric Info from Image using DL}

  \item \textbf{Overhead Image for Image Understanding}

  \item \textbf{Extract High-Level Feature by Learning When and Where.}

>>>>

\section{Our Approach}
My thesis focuses on the image understanding with camera geometry.
There are two directions we will address: 1) How can we obtain camera
geometry from images; 2) How can we use camera geometry to improve the
current methods for image semantic extracting. For the first direction,
we explore both the traditional method and deep learning approaches on
different geometric calibration parameters. For the second direction,
we will exploit the image geometric location to help extract
semantically meaningful informations from images.

@@

  \item \textbf{Complete Camera Geo-Calibration with MCMC Method:} 
  The complete camera geo-calibration includes the detection of camera
  location in the world, the pose and the focal length of the camera
  given the input image. By constructing a objective function that
  measures the ``matchness'' between the camera calibration and the
  observation of the image, we are able to optimize the parameters in
  the calibration space. However, this space multi-dimensional, which
  makes the naive grid search infeasible. Our insight is to do the
  optimization using Markov Chain Monte Carlo (MCMC) method. Our
  algorithm is able to avoid unnecessary sampling in the
  low-probabilistic region in the parameter space thus reduce the
  computational time dramatically.

  \item \textbf{Detecting Horizon and VPs using CNN:}
  Horizon line and vanishing points (VPs) plays important roles in many
  application such as image mensuration and facade detection. In the
  previous work, researchers tended to use build bottom-up approaches to
  solve this problem. Our work is inspired by human's perception of the
  horizon line and the vanishing point. Our method exploit the image
  global context to provide a prior distribution of the final solution,
  thus to reduce the dimensionality of the solution space.

  \item \textbf{Cross-view Domain Adaptation:} 
  Current machine learning methods address problems that involves mostly
  the ground imagery. Tons of dataset targeting on ground imagery are
  annotated while much fewer are done for the overhead imagery.
  In this work, we try to transfer the semantics from the ground imagery
  to the overhead imagery by identifying the latent geometry
  correspondences between these two. Similar to methods that driven by
  the projection losses \todo{citation}, our network learns 
  both the geometric projection between the overhead and ground
  images, and the semantics of the overhead images jointly.

  \item \textbf{Extract High-Level Feature by Learning When and Where:}
  One of the key to the success of machine learning approaches are the
  large quantity of annotated data. However, fully annotated imagery
  only consists of a tiny part of the image resources available online.
  The idea is to exploit other meta-info that are automatically
  recorded/captured by devices to train the ML models.  We demonstrate
  that the camera geometry can be used as weak ground truth for
  supervision problem. By learning the capture time and the geolocation
  of the images, our network is able capture the geo-temporal related
  high-level features.
